A Failure Detection Approach of Data Center Networks\titlenote{(Produces the permission block, and copyright information). For use with SIG-ALTERNATE.CLS. Supported by ACM.}

### 2016-07-03 SIG Proceedings Template-Jan2015 Zip/paper.tex
writing Introduction part

\section{Introduction}
Data center.

The rest of the paper is organized as follows. Section 2 discusses related work. Section 3 presents data center networks architecture. Section 4 provides an overview of our approach, while the details are described in Section 5. The experimental evaluation along with experiments results is presented in Section 6. Finally, Section 7 concludes this paper.

@@

\begin{equation}
S_{ToR,t}=\left\{
    \begin{array}{lcl}
    \text{suspect} & \text{if} & |\left\{s|s\in ToR\right\} \cap \left\{s|S_{s,t}=\text{suspect}\right\}| \\
    && \geq \alpha \cdot m\\
    \text{trust} && \text{otherwise}
    \end{array}
\right.
\end{equation}
where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion is to determine failure of a ToR. When \textbf{Crash Decider} gets more than $\alpha \cdot m$ crash report messages of servers under the ToR crash, it will report the crash of ToR. The last specification in Section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure. An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.

To sum up, Algorithm 1 illustrates the pseudo-code for overall detection algorithm of \textbf{Crash Decider}.

\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{Detection Algorithm of \textbf{Crash Decider}}
	%\label{alg0}
	\begin{algorithmic}[1]
		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
		\ENSURE $S_{i,t}$, $i$ is an imperative device

@@

\section{Evaluation}
In this section, we will present how we evaluate our approach in terms of efficiency and effectiveness. Experiments results will also be shown in this section.

@@

\subsubsection*{RQ2: Can K-detectors model benefit ToR crash detection?}
\quad The evaluation of failure detection for ToRs is almost the same as servers. We will evaluate the impact of different values of $\alpha$.

@@

\subsection{Experiments Results}

@@

\subsubsection*{RQ2: ToR crash Detection}
\quad To answer this question,

The drawback of our approach is that once occurring ToR failures, we cannot detect server crashes within the rack before the ToR recovering.

\subsubsection*{RQ3: QoS of BPNN Based Model?}
\quad To answer this question, we wants to firstly explain why we select BPNN rather other popular classifiers. We select 3 other algorithms including Decision Tree (C4.5) \cite{quinlan2014c4}, Bayesian Networks (BN) \cite{jensen1996introduction} and Support Vector Machine (SVM) \cite{scholkopf1999advances}. We apply these algorithms to train data by 10-fold cross-validation. Results are all shown in Table 1. Obviously BPNN outperforms other algorithms.

@@

On the other hand, there is a huge improvement in terms of DS. The approach proposed by Herodotou et al. tends to assign a wider range of failure scores to multiple links, while our approach is better at finding the relevant links. It mainly stems from the fact that our approach is based on a multi-layer perceptron architecture, it can precisely capture the characteristic of each link failure. But one of the drawbacks of our approach is that it requires much data and time to train BPNN offline to ensure its generalization ability, it cannot adapt to network topology changes as well.

>>>>

\section{Introduction}
Data center is a pool of resources interconnected using a communication network, a broad range of services (e.g., Web search, data analytic, storage backup) are hosted on data centers. Data center networks play a pivotal role in data centers as they integrate various resources and connect hundreds of thousands devices together (e.g. routers, switches, servers). Due to the scale of data center networks, failures are common and hence automated failure detection can help reduce mean-time-to-recovery and service disruption.

However, failure detection in data center networks should not be simplex. On one hand, data center networks are reliable \cite{gill2011understanding} due to the built-in redundancy of data center networks like hardware redundancy and fault-tolerant routing protocols. For about 80\% of the links and about 60\% of the devices, there is a more than four 9's of availability. On the other hand, many applications hosted on data centers have very strict timing constraints \cite{tomsic20152w}, they require failure detectors to provide quality of service (QoS) with quantitative timeliness guarantees.

Unfortunately, few researches have noticed QoS difference in failure detection in data center networks. Some researches on failure detection architecture such as \cite{felber1999failure} \cite{van1998gossip} \cite{gillen2007scalable} \cite{xu2012smart} \cite{xu2012smart} focus on scalable node or process failure detection in large scale distributed systems without considering underlying network topologies. Other failure detection approaches \cite{bahl2007towards} \cite{herodotou2014scalable} \cite{kandula2005shrink} treat all the network devices equally.

Having realized the limitations of existing work and also to address this issue, we firstly divide network devices into two categories: imperative devices and non-imperative devices. including servers, top of rack switches and links between them

This paper makes the following contributions:
\begin{itemize}
  \item To the best of our knowledge, 
  \item 
  \item 
\end{itemize}

The rest of the paper is organized as follows. Section 2 discusses related work. Section 3 presents data center networks architecture. Section 4 provides an overview of our approach, while the details are described in Section 5. The experimental evaluation along with experimental results is presented in Section 6. Finally, Section 7 concludes this paper.

@@

\begin{equation}
S_{ToR,t}=\left\{
    \begin{array}{lcl}
    \text{suspect} & \text{if} & | \{s | s \in ToR, \\
    && CRMO_{s,t} \not = \emptyset, \\
    && |CRM_{s,t}|=1\} | \geq \alpha \cdot m \\

    \text{trust} && \text{otherwise}
    \end{array}
\right.
\end{equation}
where $m$ is the number of servers per rack, $\alpha$ is a  proportionality coefficient measuring how strict the criterion is to determine failure of a ToR. $CRMO_{s,t}$ denotes the collection of crash report messages of $s$ coming from outside racks until time $t$. When \textbf{Crash Decider} gets more than $\alpha \cdot m$ crash report messages of servers under the ToR crash, it will report the crash of ToR. The last specification in Section 5.2 ensures that once a ToR is down, each other rack has the chance to find this failure. An extreme counter-example is that if the outside detectors of rack 1 servers are all in rack 2, once ToR of rack 2 is down, \textbf{Crash Decider} never perceives the status of ToR of rack 1.

\subsubsection*{Upper Bound of $\alpha$}
Theoretically, a smaller $\alpha$ means a more aggressive detection. We can set an appropriate $\alpha$ empirically by looking back on historical data on ToR crashes. Suppose we have known the ToR crash probability $p$, there are $n$ racks (each one has a ToR) and crashes of ToRs are subject to \textit{binomial distribution}:
\begin{equation}
    \begin{aligned}
        &m_0  = \frac{m}{n-1}(n-k_0) = \frac{m(n-k_0)}{n-1}\\
        &\alpha \leq \alpha_0  = \frac{m_0}{m} = \frac{n-k_0}{n-1}\\
        &\text{where } k_0 \text{ is the minimum of } k\\
        & s.t. \quad Pr(x\leq k) = \sum_{r=0}^k C_n^r p^r(1-p)^{n-r} \geq p_0 \\
    \end{aligned}
\end{equation}
$Pr(x\leq k)$ denotes the probability of number of ToR crashes is no more than $k$, $m_0$ is the number of observed crash report messages, it equals to number of alive ToRs times number of detectors per rack. Consequently, given $p$ and $p_0$, the theoretical upper bound of $\alpha$ should be $\alpha_0$.

To sum up, Algorithm 1 illustrates the pseudo-code for overall detection algorithm of \textbf{Crash Decider}.
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\begin{algorithm}
	\caption{Detection Algorithm of \textbf{Crash Decider}}
	%\label{alg0}
	\begin{algorithmic}[1]
		\REQUIRE $K$, $\eta$, $n$, $\alpha$, $m$, $\tau_m$
		\ENSURE $S_{i,t}$, $i$ is an imperative device

@@

\section{Evaluation}
In this section, we will present how we evaluate our approach in terms of efficiency and effectiveness. Experimental results will also be shown in this section.

@@

\subsubsection*{RQ2: Can K-detectors model benefit ToR failure detection?}
\quad The evaluation of failure detection for ToRs is similar to servers. We will evaluate the impact of different number of server crashes, that is to say, we want to see whether server failures affect the QoS of ToR failure detection. The evaluation metrics are the same as servers.

@@

\subsection{Experimental Results}

@@

\subsubsection*{RQ2: ToR crash Detection}
\quad To answer this question, we compute the metrics of ToRs failure detection in the presence of different server crashes. On top of this, we randomly make three ToR failure events with failure group size equals to 1, 2 and 3 respectively. In particular, $\alpha$ is set to 0.9, 0.6 and 0.4 when failure group size is 1, 2 and 3 respectively.

The $P_A$ and $AD_T$ are shown in Figure 8. Roughly speaking, size of server crashes has little impact on QoS of ToR failure detection. With the increasing of ToR crashes number, $AD_T$ is better due to a smaller $\alpha$, which means \textbf{Crash Decider} needs fewer crash report messages to determine the failure of a ToR.

\begin{figure}
  \centering
  \begin{tabular}{c}
  \includegraphics[scale=0.7]{tor-r1} \\
  \includegraphics[scale=0.7]{tor-r2} \\
  \end{tabular}
  \caption{Effect of Server Crashes on $P_A$ and $AT_D$ of ToRs}
\end{figure}

The main drawback of our approach is that once occurring ToR failures, we cannot detect server crashes within the rack before the ToR recovers.

\subsubsection*{RQ3: QoS of BPNN Based Model}
\quad To answer this question, we wants to firstly explain why we select BPNN rather other popular classifiers. We select 3 other algorithms including Decision Tree (C4.5) \cite{quinlan2014c4}, Bayesian Networks (BN) \cite{jensen1996introduction} and Support Vector Machine (SVM) \cite{scholkopf1999advances}. We apply these algorithms to train data by 10-fold cross-validation. Results are all shown in Table 1. Obviously BPNN outperforms other algorithms.

@@

On the other hand, there is a huge improvement in terms of DS. The approach proposed by Herodotou et al. tends to assign a wider range of failure scores to multiple links, while our approach is better at finding the relevant links. It mainly stems from the fact that our approach is based on a multi-layer perceptron architecture, it can precisely capture the characteristic of each link failure. But one of the drawbacks of our approach is that it requires much data and time to train BPNN offline to ensure its generalization ability, it cannot adapt to network topology changes either.
